INTELLIGENT SYSTEMS

### 2021-03-27 paper_2.tex
finish 2.3.2

\subsection{COMPARATIVE EXPERIMENTS}
In order to evaluate the quantitative goodness of the proposed algorithm, 
three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
recreation (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The goal 
is to have high values in all three metrics. A low percentuage of UE indicates 
that the boundarye isn't costituted only by the pixels that form it, but is 
also made up of pixels that belong to other objects. A segmentation is correct 
when at least two boundary pixel fall from at least one superpixel boundary 
point. A high BR index indicates that the better segmentation is obtained. 
On the other hand, the ASA metric indicates the level of accurancy achieved 
in the segmentation pashe of contour, obtained thanks to the various labels 
(ground-truth) placed on each superpixel. A high ASA value indicates that 
superpixel adapt well to objects. The experiments were conducted on a set 
of 300 images belonging to the Barkeley Segmentation Database \cite{0781426515}.

\subsubsection{Parameter Selection}
When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to 
be aggregated into a single cluster, forming superpixels with a regular shape 
and therefore potentially incorrect. On the other hand, when \emph{r} is small, then 
it means that the pixels tend to have similar colors, therefore both will be 
grouped into a single cluster, forming irregular superpixels. Therefore \emph{r} 
can be used as a correction parameter. In order to control the search range 
of the K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at 
least 0.5. This value will be multiplied by the spatial components, vertical 
($ v_x $) and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
as this parameter increases, the size of each superpixel generated and the 
general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ 
is set to 1.

\subsubsection{Comparison With State-of-the-Art}
The proposed system is compared with other existing superpixels algorithms 
in the state of the art. A comparison, in terms of boundary adherence and 
speed in segmentation, is shown in table () when the number of superpixels 
\emph{K} generated is 400. With a relatively high \emph{K} number, LSC achieves 
the best performance.

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
        \hline
        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
        \hline
        \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
        \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
        \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
        \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
        \hline
        \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
        \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
        \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Performance metrics superpixel segmentation algorithms at K=400}
    \label{table superpixels}
\end{table}

>>>>

\subsection{COMPARATIVE EXPERIMENTS}
In order to evaluate the quantitative goodness of the proposed algorithm, 
three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The 
goal is to have a low UE value, while it is preferable to have high values in BR 
and ASA. A low percentage of UE indicates that the detected boundary is made 
up of a small amount of pixels not belonging to the object to be delimited. 
A segmentation is correct when at least two boundary pixel fall from at least 
one superpixel boundary point. A high BR index indicates that the better 
segmentation is obtained. On the other hand, the ASA metric indicates the 
level of accurancy achieved in the segmentation pashe of contour, obtained 
thanks to the various labels (ground-truth) placed on each superpixel. A 
high ASA value indicates that superpixel adapt well to objects. The experiments 
were conducted on a set of 300 images belonging to the Barkeley 
Segmentation Database \cite{0781426515}.

\subsubsection{Parameter Selection}
When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to be 
aggregated into a single cluster, forming superpixels with a regular shape 
and therefore potentially incorrect. On the other hand, when \emph{r} is small, 
then it means that the pixels tend to have similar colors, therefore both 
will be grouped into a single cluster, forming irregular superpixels. In order to 
choose an optimal r value, it is necessary to introduce a metric that calculates 
the average  values of shape regularity. The average value of shape regularity 
is measured with a metric called superpixel compactness \emph{(CP)} \cite{0781426533} which is 
inversely proportional to the BR index. So as CP increases, the likelihood 
of regular shapes being created is greater and at the same time worse segmentation 
will be generated as BR decreases. The r value will be chosen 
when the value resulting from $ (1-BR / CP) $ is the lowest. Therefore \emph{r} can be 
used as a correction parameter. In order to control the search range of the 
K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at least 
0.5. This value will be multiplied by the spatial components, vertical ($ v_x $) 
and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
as this parameter increases, the size of each superpixel generated and the 
general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ is 
set to 1.

\subsubsection{Comparison With State-of-the-Art}
The proposed system is compared with other existing superpixels algorithms 
in the state of the art. A comparison, in terms of boundary adherence and 
speed in segmentation (Table \ref{table superpixels}), when the number of superpixels \emph{K} generated 
is 400. With a relatively high \emph{K} number, LSC achieves the best 
performance.

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
        \hline
        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
        \hline
        \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
        \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
        \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
        \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
        \hline
        \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
        \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
        \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Performance metrics superpixel segmentation algorithms at K=400}
    \label{table superpixels}
\end{table}
As we can see from the results, the worst algorithm, in terms of time, 
is \emph{NCuts}, while a good algorithm, which ranks second before \emph{LSC}, is \emph{SLIC}. 
Unlike the algorithm studied, SLIC uses an iterative K-means clustering 
performed inside different feature spaces, based only on local characteristics. 
On the other hand, LSC is able to use local and global features thanks to the 
$ \phi $  mapping function, all to have a better segmentation. Looking at the data 
in the table, this makes us understand how LSC is able to have a better BR 
value despite having a higher CP value than the previous algorithms, this 
represents the strength of this algorithm.
